Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-10-24 MHCpaper/MHCsupp.tex
scan & chr2 figs

>>>>

\hypertarget{par:pooled_scan}{To} verify that this always happens, we scanned over acceptable values of the six parameters relevant to gain-decrease pre-training in wild-type models: $q\pot$, $q\dep\lmin < q\dep\lmax$, and $f\dep\dec < f\dep\norm < f\dep\inc$.
Each parameter was scanned over 10 values from 0.05 to 0.95, rejecting values that do not respect the inequalities above.
For each parameter set, we computed the initial learning rate, $\dot{L}(0)$ from \eqref{eq:learning}, with and without pre-training.
To qualitatively reproduce the experimental results, we would need $\dot{L}_\text{no pre} - \dot{L}_\text{pre} > 0$ at $t = 0$.
The range of values obtained is plotted in \autoref{fig:pooled_scan}, where we see that this difference is always negative, ruling out this model.

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=0.4\linewidth]{pooled_deponly_scan.eps}
  \caption{Difference in initial learning rate in wild-type models, without and with gain-decrease pre-training.
  Learning, $L(t)$ is defined in \eqref{eq:learning}.
  Here, we show the maximum and minimum values of this quantity when scanning all 6 relevant parameters (see \protect\hyperlink{par:pooled_scan}{text}).
  We see that this quantity is always negative, whereas it was positive in the experiments.
  }\label{fig:pooled_scan}
\end{figure}
